---
title: "Env Contamination Update"
author: "Casey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    # toc: yes
    # toc_float: true
    # number_sections: true
  # pdf_document:
    # toc: yes
---

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)

# Import data:
source("helper_dataload_all.R")
source("helper_graph.R")
source("helper_graph_combined.R")


# data setup (adding country and city names etc.)
df.ecdata <- df.ecdata %>% 
        left_join(., meta_sampleID, by = c("sample_type" = "id")) %>%
        left_join(., meta_dply[, c("id", "country", "city", "citylabel")], by = c("dply_num" = "id"))

# check:
# levels(df.ecdata$sample_type_name)
# factor(meta_dply$citylabel)

# alternative drinking water declarations
# add dw level for factors
# df.ecdata$col_sample_type_alt <- factor(df.ecdata$col_sample_type_alt, 
#                                         levels=levels(df.ecdata$col_sample_type_alt))

# df.ecdata$col_sample_type_alt[df.ecdata$sample_type == 3 & df.ecdata$col_sample_type_alt == ""] <- "Drinking Water"

#recode other drinking water
# df.ecdata$sample_type[df.ecdata$sample_type == 3 & df.ecdata$col_sample_type_alt != "Drinking Water" 
#                       & df.ecdata$col_sample_type_alt != "" ] <- 33


df.col <- df.col %>% left_join(., meta_dply[c("id", "citylabel")], by = c("dply_num" = "id"))
df.lab <- df.lab %>% left_join(., meta_dply[c("id", "citylabel")], by = c("dply_num" = "id"))
df.h <- df.h %>% left_join(., meta_dply[c("id", "citylabel")], by = c("dply_num" = "id"))
df.c <- df.c %>% left_join(., meta_dply[c("id", "citylabel")], by = c("dply_num" = "id"))
df.s <- df.s %>% left_join(., meta_dply[c("id", "citylabel")], by = c("dply_num" = "id"))


```

# {.tabset}


## Contamination
### Stats on ec_conc

```{r echo=TRUE}


df.ecdata %>% group_by(citylabel, sample_type_name) %>% summarise("n" = n(), 
                                        "min ecoli" = round(min(log10(ec_conc), na.rm = T),2),
                                        "max ecoli" = round(max(log10(ec_conc), na.rm = T),2),
                                        "mean ecoli" = round(mean(log10(ec_conc), na.rm = T),2),
                                        "standard deviation" = round(sd(log10(ec_conc), na.rm = T),2),
                                        "variance" = round(var(log10(ec_conc), na.rm = T),2)
                                                  ) %>%
        kable(., caption = "E. coli count per deployment by pathway") %>% 
        kable_styling(bootstrap_options = c("hover", "bordered","condensed"), full_width = F, position = "left")

